An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2022-03-27 simplified_sdc_intro/paper.tex
some net information

%\documentclass[times,modern]{aastex63}
\documentclass[times,preprint]{aastex63}

@@

Our reaction network includes the nuclei: $\mathrm{n}$,
${}^{1}\mathrm{H}$, ${}^{4}\mathrm{He}$, ${}^{12}\mathrm{C}$,
${}^{14}\mathrm{C}$, ${}^{13}\mathrm{N}$, ${}^{14}\mathrm{N}$,
${}^{16}\mathrm{O}$, ${}^{18}\mathrm{O}$, ${}^{18}\mathrm{F}$,
${}^{20}\mathrm{Ne}$, ${}^{21}\mathrm{Ne}$, ${}^{22}\mathrm{Ne}$,
${}^{22}\mathrm{Na}$, ${}^{23}\mathrm{Na}$, ${}^{23}\mathrm{Mg}$,
${}^{24}\mathrm{Mg}$, ${}^{27}\mathrm{Al}$, ${}^{27}\mathrm{Si}$,
${}^{28}\mathrm{Si}$, ${}^{31}\mathrm{P}$, ${}^{31}\mathrm{S}$,
${}^{32}\mathrm{S}$, ${}^{35}\mathrm{Cl}$, ${}^{36}\mathrm{Ar}$,
${}^{39}\mathrm{K}$, ${}^{40}\mathrm{Ca}$, ${}^{43}\mathrm{Sc}$,
${}^{44}\mathrm{Ti}$, ${}^{47}\mathrm{V}$, ${}^{48}\mathrm{Cr}$,
${}^{51}\mathrm{Mn}$, ${}^{52}\mathrm{Fe}$, ${}^{55}\mathrm{Co}$,
${}^{56}\mathrm{Ni}$.

The rates linking them are:

@@

\tablecaption{\label{table:react_converge_strang} Convergence ($L_1$ norm) for the reacting convergence problem using Strang splitting.}

>>>>

%\documentclass[times,modern]{aastex63}
%\documentclass[times,preprint]{aastex63}
\documentclass{aastex63}

@@

We build a reaction network that approximates an $\alpha$-chain,
including all $\isotm{He}{4}$, and all of the $\alpha$ nuclei from
$\isotm{C}{12}$ to $\isotm{Ni}{56}$.  We want to capture both the
$(\alpha,\gamma)$ and $(\alpha,p)(p,\gamma)$ links, so we include the
intermediate nuclei from the $(\alpha,p)$ rate instead of
approximating these links assuming proton equilibriation.  
Following \citet{shenbildsten}, we include the sequences
$\isotm{C}{13}(\alpha,\gamma)\isotm{O}{18}(\alpha,\gamma)\isotm{Ne}{22}$
and $\isotm{N}{14}(\alpha,\gamma)\isotm{F}{18}(\alpha,
p)\isotm{Ne}{21}$, which produce the protons that can allow for
$\isotm{C}{12}(p, \gamma)\isotm{N}{13}(\alpha, p)\isotm{O}{16}$ to compete
with $\isotm{C}{12}(\alpha,\gamma)\isotm{O}{16}$.  We add $\isotm{Na}{22}$
to link the $\isotm{Ne}{21}$ produced back to the $\alpha$-chain.  We grab
all of the ReacLib \citep{reaclib} reaction rates linking these nuclei using \pynucastro~\citep{pynucastro}.
We are missing one rate each for $\isotm{C}{12} + \isotm{C}{12}$,
$\isotm{C}{12} + \isotm{O}{16}$, and $\isotm{O}{16} + \isotm{O}{16}$
    involving neutron production followed by a capture back to one of
    our $\alpha$-chain nuclei, so we explicitly add these rates as
    well.

Our final set of nuclei are $\mathrm{n}$, ${}^{1}\mathrm{H}$,
${}^{4}\mathrm{He}$, ${}^{12}\mathrm{C}$, ${}^{14}\mathrm{C}$,
${}^{13}\mathrm{N}$, ${}^{14}\mathrm{N}$, ${}^{16}\mathrm{O}$,
${}^{18}\mathrm{O}$, ${}^{18}\mathrm{F}$, ${}^{20}\mathrm{Ne}$,
${}^{21}\mathrm{Ne}$, ${}^{22}\mathrm{Ne}$, ${}^{22}\mathrm{Na}$,
${}^{23}\mathrm{Na}$, ${}^{23}\mathrm{Mg}$, ${}^{24}\mathrm{Mg}$,
${}^{27}\mathrm{Al}$, ${}^{27}\mathrm{Si}$, ${}^{28}\mathrm{Si}$,
${}^{31}\mathrm{P}$, ${}^{31}\mathrm{S}$, ${}^{32}\mathrm{S}$,
${}^{35}\mathrm{Cl}$, ${}^{36}\mathrm{Ar}$, ${}^{39}\mathrm{K}$,
${}^{40}\mathrm{Ca}$, ${}^{43}\mathrm{Sc}$, ${}^{44}\mathrm{Ti}$,
${}^{47}\mathrm{V}$, ${}^{48}\mathrm{Cr}$, ${}^{51}\mathrm{Mn}$,
${}^{52}\mathrm{Fe}$, ${}^{55}\mathrm{Co}$, ${}^{56}\mathrm{Ni}$.  The 119
rates linking them are given in table ~\ref{table:rates}, with the
forward rates having a positive $Q$ value and the reverse having a
negative $Q$ value.  We add screening to the rates using the prescription
from The C++ code for the network is output by \pynucastro\
directly for \castro.  A graphical overview of the network showing the links
between the nuclei is shown in figure~\ref{fig:subch_network}.

@@

\tablecaption{\label{table:rates} Reaction rates included in our network.}
